Exploratory Analysis

### 2021-11-27 eda-h.Rmd
Creating some plots

@@

```{r}
ggpairs(train)
```

>>>>

train$ChestPainType <- as.factor(train$ChestPainType)
train$Sex <- as.factor(train$Sex)
train$FastingBS <- as.factor(train$FastingBS)
train$RestingECG <- as.factor(train$RestingECG)
train$ExerciseAngina <- as.factor(train$ExerciseAngina)
train$ST_Slope <- as.factor(train$ST_Slope)
train$HeartDisease <- as.factor(train$HeartDisease)

@@

```{r}
p1 <- ggplot(train,aes(x=Age,y=HeartDisease))+ geom_boxplot()+coord_flip()

p2 <-ggplot(train,aes(x=Sex,fill=HeartDisease))+ geom_bar(position = "dodge")

p3 <-ggplot(train,aes(x=ChestPainType,fill=HeartDisease))+ geom_bar(position = "dodge")

p4<- ggplot(train,aes(x=RestingBP,y=HeartDisease))+ geom_boxplot()+coord_flip()

ggarrange(p1,p2,p3,p4)
```

```{r}
p1 <- ggplot(train,aes(x=Cholesterol,y=HeartDisease))+ geom_boxplot()+coord_flip()

p2 <-ggplot(train,aes(x=FastingBS,fill=HeartDisease))+ geom_bar(position = "dodge")

p3 <-ggplot(train,aes(x=RestingECG,fill=HeartDisease))+ geom_bar(position = "dodge")

p4<- ggplot(train,aes(x=MaxHR,y=HeartDisease))+ geom_boxplot()+coord_flip()

ggarrange(p1,p2,p3,p4)
```
